Equalizer\\Programming and User Guide

### 2013-03-07 Developer/ProgrammingGuide/paper.tex
Add documentation for co::ObjectMap (Eyescale/Collage#17)

>>>>

\subsection{ObjectMap}

The \textsf{co::ObjectMap} is a specialized \textsf{co::Serializable} which
provides automatic distribution and synchronization of \textsf{co::Object}s.
All changed objects are committed when \textsf{co::ObjectMap} is committed, and
sync() on slave instances updates mapped objects to their respective versions.

The objects on slave ObjectMap instances are mapped explicitly, either by
providing an already constructed instance or using an implicit object creation
using \textsf{co::ObjectFactory}. The factory needs to be supplied upon
construction of \textsf{co::ObjectMap} and the implementation for creating the
desired object types. Implicitly created objects are owned by the object which
affects the lifetime of those objects considering unmapping operations caused
by deregister(), explicit unmapping or destruction of the slave instance
ObjectMap.

In Sequel, the \textsf{co::ObjectMap} is used to distribute and synchronize the
InitData and FrameData objects. Sequel adds the object IDs for both objects in
addition to the default ObjectMap for automatic mapping during first access.
The main advantage comes from the one point commit and synchronization which
automatically updates changed objects to their correct version.
